What We Eval in the Shadows

### 2021-07-08 paper/main.tex
Expand Morandat et al comparison

\citet{ecoop12} had a short section on the usage of \eval in R. They found the
that \eval  is widely used in R code with 8500 call sites in CRAN and 2.2 million dynamic calls. The 15 most frequent call sites account for 88\% of those. The
\c{match.arg} function is the highest used one with 54\% of all calls. In the
other call sites, they saw two use cases. The most common is the evaluation of
the source code of a promise retrieved by \c{substitute} in a new environment,
\eg as done in the \c{with} function. The other use case is the invocation of a
function whose name or arguments are determined dynamically. For this purpose, R provides \c{do.call} and thus \eval is overkill.

>>>>

\citet{ecoop12} had a few paragraphs on the usage of \eval in R. They found the
that \eval  is widely used in R code with 8500 call sites in 1238 CRAN packages and 2.2 million dynamic calls.   The 15 most frequent call sites account for 88\% of those. The
\c{match.arg} function is the highest used one with 54\% of all calls. In the
other call sites, they saw two use cases. The most common is the evaluation of
the source code of a promise retrieved by \c{substitute} in a new environment,
\eg as done in the \c{with} function. The other use case is the invocation of a
function whose name or arguments are determined dynamically. For this purpose, R provides \c{do.call} and thus \eval is overkill. Our corpus is larger, with \CranPackages packages, \packageTriggeredpkgs packages with at least one \eval, for a total of \PkgHitEvalCallSites sites and \packageAllcallsRnd dynamic calls, although they also looked at the Bioconductor package repository\footnote{\url{https://www.bioconductor.org/}} in addition to CRAN. We also track much more runtime information on the \eval calls during tracing. It enables us to have a more nuanced and accurate picture, and identify more diverse use cases of \eval.
